Sperm should evolve to make female meiosis fair.

### 2014-05-16 writeup_and_notes/male_dependent_drive.tex
small changes to intro

We develop population genetic models exploring the evolution of sperm influence on female meiotic drive. %, focussing on models in which `self-promoting' alleles in sperm facilitate drive of like genotypes during gametogenesis in heterozygous females. 
\yb{We first focus on models in which `self-promoting' alleles in sperm facilitate drive of like genotypes during gametogenesis in heterozygous females. }
%In this article we explore through simple population genetic models the consequences of alleles that influence the outcome of female meiosis.
These models show that sperm modifiers of female meiotic drive are
	unlikely to create a sustained conflict, and therefore 
	female meiosis will have little incentive to evolve resistance to them.
\yb{We then examine models in which an allele in sperm acts to modify the efficacy of a polymorphic meiotic driver - 
	which universally reveal that sperm acting drive modifiers are favored only if the suppress drive. }
The results highlight the fact that the interests of sperm and egg  genomes' are often aligned, as both are invested in the fate of the resultant zygote (as was speculated for the \emph{In} locus \citep{Pomiankowski1993}).
Therefore, there is little selective benefit to females in preventing sperm to influence female meioses.
\yb{Rather, features of o\"{o}genesis  may evolve to facilitate an interaction with sperm %with female meiosis
	as yet another mechanism to enforce an equitable transfer of genetic material.}

>>>>

We develop population genetic models exploring the evolution of sperm influence on female meiotic drive. %, focussing on models in which `self-promoting' alleles in sperm facilitate drive of like genotypes during gametogenesis in heterozygous females. 
We first focus on models in which `self-promoting' alleles in
  sperm facilitate drive of like \gc{alleles} during gametogenesis in heterozygous females. 
%In this article we explore through simple population genetic models the consequences of alleles that influence the outcome of female meiosis.
These models show that sperm modifiers of female meiotic drive are
	unlikely to create a sustained genomic conflict, and therefore 
	female meiosis will have little incentive to evolve resistance to them.
We then examine models in which an allele in sperm acts to modify the efficacy of a polymorphic meiotic driver - 
	which universally reveal that sperm acting drive modifiers are favored only if the suppress drive. 
The results highlight the fact that the interests of sperm and egg  genomes' are often aligned, as both are invested in the fate of the resultant zygote (as was speculated for the \emph{In} locus \citep{Pomiankowski1993}).
Therefore, there is little selective benefit to females in preventing sperm to influence female meioses.
Rather, features of o\"{o}genesis  may evolve to facilitate an interaction with sperm %with female meiosis
	as yet another mechanism to enforce an equitable transfer of genetic material.
